\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[orange]{classic}                % idem

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Chang}
\familyname{Xu}
%\title{Curriculum Vitae}
\mobile{+86 13141200542}
\email{xuchang1215@163.com}
%% \quote{``Do what you fear, and the death of fear is certain.''\\-- Anthony Robbins}

%\phone{(312) 413-8265}                      % optional, remove the line if not wanted
%\fax{312 996 1491}                          % optional, remove the line if not wanted
%\photo[64pt]{avatar.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%% \renewcommand*{\sectionfont}{\LARGE\sffamily\monospace\slshape}
%% \renewcommand*\addressfont{\fontfamily{pzc}\selectfont}
%% \renewcommand*\sectionfont{\fontfamily{pzc}\fontsize{20}{24}\selectfont}

\begin{document}
\maketitle

\section{Education}
\cventry{2014--Present}{MS in Computer Science}{ Institute of Network Technology, Beijing University of Posts and Telecommunications}{expected 2017}{\textbf{examination free admission}}{}
\cventry{2010--2014}{BA in Software Engineering}{Software School, Beijing University of Posts and Telecommunications}{}{}{}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}

\section{Internship}
\vspace*{0.2\baselineskip}

\cventry{2014}{Baidu}{Nature Language Process Department}{iOS development}{}{Developed "BaiduTranslate" application (the version after 5.0)}
\cventry{2013}{Baidu}{Recommendations and Personalization Department}{Android development}{}{Developed mobile application based on Android : Tu Shu Bi Ji. Using OCR to help people take notes instead of writing. Support to share to social network. I was the major contributor of this project. \url{http://biji.baidu.com}}

\section{Awards}
\cventry{2013}{MCM - Mathematical Contest in Modeling}{Meritorious Winner}{}{}{}
\cventry{2012}{Intel Cup National Collegiate Software Innovation Contest}{Third prize}{}{}{}
\cventry{2012}{Lanqiao Cup Programming Competition}{Third prize, Beijing}{}{}{}
\cventry{2011}{The First Prize Scholarship}{}{}{}{}


\section{Project Experience}
%% \subsection{Research Projects}
\vspace*{0.2\baselineskip}

\cventry{2015}
{AllStar Project}
{iOS, Android}
{}{}
{AllStar is a mobile application aiming at online auditions for movie. I designed the project structure and module of this application and also developed most UI and business logic.\url{http://www.youmingxing.com}}

\cventry{2015}
{Massage Order Project: He Ping Yue Tui}
{iOS, Scala}
{}{}
{This project provides the service that users could order a massage online, and massagers use it to manipulate orders. We used Play framework to build a back-end management system. I developed the app used by massagers and the statistics module in the back-end. }

\cventry{2014}
{inHealth}
{Android}
{}{}
{inHealth is an additional app of  smart watch ‘inWatch’. We got user data througth blue tooth. My major work is development of the data module and UI.}


\section{Skills}
\cventry{Languages}{Java > Objective-C > Scala}{}{}{}{}
\cventry{Platfom}{Android, iOS}{}{}{}{}
%% \cventry{Application Dev}{Ruby on Rails, iOS development}{}{}{}{}
\cventry{English}{CET-6}{good in spoken and written English}{}{}{}
% \closesection{}                   % needed to renewcommands
% \renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

\end{document}
